Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-03-01 siip.tex
adds refs

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

          \pagestyle{fancy}
          %\pagenumbering{gobble}
          %\fancyhead[location]{text}
          % Leave Left and Right Header empty.
          %\lhead{}
          %\rhead{}
          \lhead{\textcolor{gray}{Investigator: Prof. \authorname 
          <\authoremail>}}
          \rhead{\textcolor{gray}{SIIP Pre-Proposal\\Dept. of Nuclear, 
          Plasma, and Radiological Engineering}}
          %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
          \renewcommand{\headrulewidth}{0pt}
          \renewcommand{\footrulewidth}{0pt}
          \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

          \section{The Problem}
          As you read this, thousands of professors in the United States are 
          simultaneously preparing lessons on transposing a matrix.
          They are doing so largely without recieving feedback from one another 
          or directly building on one another's experience 
          \cite{wilson_software_2014}. In this way, professors spend an enormous amount of time 
          duplicating curriculum development efforts already tackled 
          by colleagues. What's worse is that these efforts are 
          rarely, if ever, reviewed by, shared with, or extended upon by 
          peers.

          Wikipedia and open source software development provide excellent 
          examples of distributed expert collaboration and dynamic peer review 
          on a master product. So, why aren't professors sharing their lesson 
          materials online, collaborating on canonical lesson sets, 
          diffing and merging similar lessons, and reviewing one another's 
          work? \emph{Our goal is to explore the possibility that curriculum development for 
          university courses can operate like open source software development 
          does.}

          \section{The Proposed Solution}
          We propose a proof-of-concept for collaborative, open source, 
          curriculum development to improve the transfer of lessons learned 
          between instructors of the same course (either at a single university or 
          among different campuses). This small-scale prototype collaboration 
          will provide a framework which could be adopted for collaboration among faculty 
          teaching courses with an inherently larger scale (e.g. CS101).

          This initiative already involves a few peer professors. Six faculty 
          in Nuclear Engineering from UC Berkeley, the University of Wisconsin 
          at Madison, Kansas State, U. South Carolina, and U. 
          Tennessee-Knoxville are involved. We all use GitHub \cite{github} to 
          store, revise, and collaborate on research, especially source code. A 
          few of us have already started to host our course curricula online as 
          well, but these are typically single author repositories 
          \cite{skutnik,wilson,slaybaugh,scopatz,borelli,roberts}.

@@

          Such projects occur drawing on a community of experts toward 
          creating a robust shared resource. In open source software, 
          developers share code revisions in online repositories, review one 
          anothers work, and contribute back their own improvements to the main 
          project.

          \paragraph{The participants will collaborate} on a master set of learning 
          modules for an upper-division course in nuclear engineering : 
          The Nuclear Fuel Cycle. In the near term, we will develop fine 
          grained learning modules which may be mixed and matched to meet the 
          learning . The curriculum will be hosted on GitHub, 
          test by all of us, and improved continually as we learn and grow as 
          instructors.

          \paragraph{Each learning module} may include active in-class exercises, 
          presentation notes, homework problems, project descriptions, and 
          evaluation tools.

          \paragraph{This challenge has been encountered} by collaborative 
          instruction organizations already. Most notable among these is 
          Software Carpentry, in which experience shows 
          \cite{wilson_lessons_2014} forks of the original material tend to diverge 
          without any strong incentive for contribution back to the master 
          material \cite{wilson_software_2014}.

          \section{The Potential Impact}
          \cite{wilson_software_2014}.

          \paragraph{We expect that} fine-grained modularity of lesson components and a clear dependency graph of prerequisite modules for each lesson may assist in overcoming this goal. Further, a small 
          and devoted group of like-minded nuclear engineering professors 
          should be able to compromise on a cohesive set of modular materials 
          that can be mixed and matched according to individual preference.

          This work will provide an important proof of concept for groups of 
          instructors willing to collaborate on open source curriculum for:
          \begin{itemize}
                  \item core courses with many sections in a single university
                  \item niche courses taught by a select group of professors across 
          universities
                  \item fundamental courses in small fields (e.g. nuclear engineering)
          \end{itemize}

          Through exploration of the option space, we will arrive at a raw 
          curriculum format for each type of learning module.

          \bibliographystyle{katyunsrt}
          \bibliography{bibliography}

          \section{Departmental Support}
          The Department of Nuclear, Plasma, and Radiological Engineering will 
          support this work with relese time through startup funds. 
          Additionally, NPRE will support workshop activities through 
          administrative effort and by providing space.
          \end{document}

>>>>

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[hidelinks]{hyperref}

@@

          \pagestyle{fancy}
          %\pagenumbering{gobble}
          %\fancyhead[location]{text}
          % Leave Left and Right Header empty.
          %\lhead{}
          %\rhead{}
          \lhead{\textcolor{gray}{PI: \authorname (NPRE)\\\authoremail}}
          \rhead{\textcolor{gray}{SIIP Pre-Proposal\\}}
          %\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
          \renewcommand{\headrulewidth}{0pt}
          \renewcommand{\footrulewidth}{0pt}
          \fancyfoot[C]{\footnotesize \textcolor{gray}{\authorsite}}

          \subsection*{Problem}
          At this very moment, hundreds of professors in the United States are 
          simultaneously preparing lessons on transposing a matrix.
          They are doing so largely without receiving feedback from one another 
          or directly building on one another's experience 
          \cite{green_building_2014}. In this way, 
          professors spend an enormous amount of time duplicating curriculum 
          development efforts already tackled by colleagues. What's worse is 
          that these efforts are rarely, if ever, reviewed by, shared with, or 
          extended upon by peers.

          Open source software development provides an excellent 
          example of a possible solution.
          These communities have mastered distributed expert collaboration, 
          dynamic peer review, and de-duplication of effort. In open source 
          software, developers share code revisions in online repositories, 
          review one another's work in small chunks \cite{wilson_best_2014}, 
          and contribute back their own improvements to the main project.

          So, why aren't professors sharing their lesson materials online, 
          collaborating on canonical lesson sets, diffing and merging similar 
          lessons, and reviewing one another's learning materials? \textbf{Our 
          goal is to explore the possibility that curriculum development for 
          university courses can operate like open source software development 
          does.}

          Attempts at this have been made before. Most notable among 
          these is Software Carpentry (which with the PI is quite involved). 
          Unfortunately, our experience showed that 
          forks of the original material tend to diverge without any strong 
          incentive for contribution back to the master material 
          \cite{wilson_software_2014,wilson_software_2014-1}. We expect that fine-grained modularity 
          of lesson components and a clear dependency graph of prerequisite 
          modules for each lesson may assist in overcoming the challenges 
          encountered by Software Carpentry and others.

          \subsection*{Proposed Solution}
          We propose a small-scale proof-of-concept for collaborative, open 
          source, curriculum development to improve the transfer of lessons 
          learned between instructors of the same course (either at a single 
          university or among different campuses). This prototype collaboration 
          will provide a template which could be adopted for collaboration 
          among faculty teaching courses with an inherently larger scale (e.g. 
          CS101).

          Faculty in Nuclear Engineering from four institutions\footnote{P.  
          Wilson at (UW Madison),Steven Skutnik (UT Knoxville), J. Roberts 
          (Kansas State University), Anthony Scopatz (University of South 
          Carolina)} have agreed to be participants in 
          this prototyping effort. We all currently use 
          \href{https://github.com}{GitHub} to store, 
          revise, and collaborate on research, especially source code. 
          Additionally, this select group already started to host our course 
          curricula online as well, but these are typically single author 
          repositories (e.g. \cite{huff_npre412_2017}).

          The participants will collaborate on a master set of learning 
          modules for an upper-division course in nuclear engineering : 
          The Nuclear Fuel Cycle. In the near term, we will develop fine 
          grained lessons which may be mixed and matched to meet the 
          learning objectives. The curriculum will be hosted on GitHub, 
          tested by all of us, and improved continually.

          \paragraph{A two-day kick-off workshop (\$15K)} at UIUC will allow the 
          participants to sketch the initial framework of 
          the collaboration and coordinate logistics. The workshop will 
          deliver:

          \begin{itemize} 
                  \item learning objectives\cite{bloom_bloom_1984} and a concept 
                          map\cite{novak_concept_1990} for the course
                  \item a list of fine-grained lesson topics
                  \item a directed acyclic graph describing dependencies among 
                          lessons
                  \item individual assignments for curriculum development
                  \item decisions to adopt specific raw formats for lesson content
                        (markdown vs. \LaTeX, Jupyter vs MATLAB, etc.)
                  \item a repository structure for organizing the lesson 
                          material (at this stage, compatibility with 
                          frameworks like RELATE 
                          \cite{kloeckner_relate_2017,kloeckner_relate_2017} 
                          and tools like PrarieLearn 
                          \cite{west_prairielearn:_2015} will be considered)
          \end{itemize}

          \paragraph{Between Workshops} work will commence on developing 
          lessons. These lessons will be submitted by pull request to the main 
          repository and each lesson will include:
          \begin{itemize} 
                  \item associated learning objectives (identified previously)
                \item content (e.g. speaking notes, presentation material, 
                        derivations, worked examples, active learning  
                          exercises, external readings, videos, images)
                  \item learning assessments (e.g. project descriptions, exam questions) 
          \end{itemize}

          Interactions will commence primarily via issues, pull requests, and 
          reviews on GitHub during this time. Meanwhile, monthly video 
          conferences will help to spur high-level conversation onward.

          \paragraph{A two-day retrospective workshop (\$15K)} at UIUC will wrap up the 
          project. Discussion concerning the process will allow reflection as 
          well as a collection of lessons learned.
          Experiences live testing the developed course material (for example 
          in NPRE412 at UIUC in Fall 2017) will be shared and suggested 
          improvements will be captures as feature requests on GitHub.  The 
          successful parts of the process will be captured a template 
          repository and collaboration instruction manual, intended for use by 
          other groups of faculty seeking to collaborate in a similar way.

          \subsection*{Potential Impact}

          This work will provide an important proof of concept for groups of 
          instructors willing to collaborate on open source curriculum for:
          \begin{itemize}
                  \item core courses with many subsections in a single university
                  \item niche courses taught by a select group of professors across 
          universities
                  \item fundamental courses in small fields (e.g. nuclear engineering)
          \end{itemize}

          \subsection*{Departmental Support}
          The Department of Nuclear, Plasma, and Radiological Engineering will 
          support this work in kind with release time for Kathryn Huff through 
          her Start-Up funds.  Additionally, NPRE will support workshop activities 
          with administrative effort and by providing space. Finally, 
          collaborating external participants will contribute in kind with 
          summer time hours.

          \bibliographystyle{katyunsrt}
          \bibliography{2017-siip}

          \end{document}

\iffalse
          New features are described in 
          tickets and discussed before implementation. Small, atomic changes 
          are reviewed before merging. Communities of practice are nurtured.

@@

\fi
